\chapter{Appendix}


\begin{fullwidth}
\textcolor[RGB]{175,0,0}{
	\LARGE This chapter should not appear in the final version of the thesis.
	}
\end{fullwidth}


\chapter*{Grading}


\section{Evaluation Criteria}

These evaluation criteria can vary depending on the topic of the thesis and are mere suggestions of important points to address.

 
\subsection{General}
\begin{itemize}
    \item Is the topic of the thesis properly tackled?
    \item Is the scientific method sound?
    \item Is the amount of work reported substantial? 
\end{itemize}

\subsection{Related work}
\begin{itemize}
    \item Is the selection of related work applicable and comprehensive?
    \item Is the current work correctly grounded in the previous literature?
    \item Is the amount and variability of previous work reported satisfactory? 
\end{itemize}

\subsection{Concept}
\begin{itemize}
    \item How novel is the concept?
    \item How is it grounded in previous work and how does it extend it? 
\end{itemize}
    
\subsection{Implementation}
\begin{itemize}
    \item How efficient and complete is the implementation based on the overall concept studied in the thesis?
    \item Did the implementation follow conventional design methods (e.g., user-centered design)?
    \item Is the structure of the implementation understandable and correctly documented?
    \item Is the implementation extensible?
\end{itemize}
     
\subsection{Study}
\begin{itemize}
    \item Are the research questions framed correctly and intelligibly?
    \item Is the type of evaluation clearly stated and justified?
    \item Is the research method described in detail and presented with regards to previous work?
    \item Are the statistical analyses adequate?
    \item Are the results appropriately presented in the thesis?
    \item Are the results appropriately discussed, specifically with respect to the presented hypotheses/questions?
\end{itemize}
    
\subsection{Content of the manuscript}
\begin{itemize}
    \item Does the abstract properly describe the contributions of the thesis?
    \item Is the thesis structured correctly and comprehensively?
    \item Is the motivation of the thesis clear?
    \item Is there a discussion of the limitations and future work of the work presented?
\end{itemize}
     
\subsection{Writing style}

\begin{itemize}
    \item Is the language used appropriate and without spelling mistakes?
    \item Does the thesis follow an internal consistency (e.g., special terms are always written in the same form)?
    \item Is the thesis presented clearly and are the means of presentation appropriate (e.g., short sentences, images are used were reasonable, images are easy to understand, etc.)?
    \item Are all figures referenced and table properly formatted?
\end{itemize}



